SBML L3 paper response to reviewers

### 2020-01-29 main.tex
Fiddle with formatting

Included below is a point-by-point explanation of our responses to the reviewers' comments; in addition, we have also included a separate document showing the detailed differences (generated with the help of latexdiff) between the manuscript of July 2019 and the new version.  The differences include additional minor corrections and updates beyond the changes made for reviewer feedback, which we have done in an effort to improve the manuscript further (for example, by reducing the overall number of citations and improving overall text cohesion).

@@

\clearpage
\emph{LATEXDIFF TO BE APPENDED HERE ...}

>>>>

Included below is a point-by-point explanation of our responses to the reviewers' comments; in addition, we have also included a separate document showing the detailed differences (generated with the help of \texttt{latexdiff}) between the manuscript of July 2019 and the new version.  The differences include additional minor corrections and updates beyond the changes made for reviewer feedback, which we have done in an effort to improve the manuscript further (for example, by reducing the overall number of citations and improving overall text cohesion).

@@
